Notes

### 2024-05-24 notes.qmd
chore: Update dependencies and remove unnecessary files

@@

@@

>>>>

---
title: Notes
jupyter: python3
---

@@

## Solar Wind Model

Sadly, JUNO does not provide plasma data during the cruise phase, so to estimate the plasma state we will use MHD model.

We are using [Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/), which models the solar wind propagation in 2D using the BATSRUS MHD solver. @keeblerMSWIM2DTwodimensionalOuter2022

Some key points about the model

-   Representing the solar wind in the ecliptic plane from 1 to 75 AU
-   2D MHD model, using the BATSRUS MHD solver
-   Inclusion of neutral hydrogen (important for the outer heliosphere)
-   Inner boundary is filled by time-shifting in situ data from multiple spacecraft

For model validation part, please see [JUNO Model Report](notebooks/20_model.ipynb).

@@

# TODOs

Science part

-   Analysis
    -   [ ] Contribution of discontinuities to the power spectrum
    -   [ ] Check Datagap
    -   [ ] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
    -   [ ] Distribution of \|B\| over radius
    -   [ ] JUNO from 2012-09\~2012-10 lack of IDS and extreme large thickness
    -   [ ] Wind data
    -   [ ] Add error bar
    -   [ ] Validate the effects of calibrate candidate duration
    -   [ ] Validate model density with `Voyager`
-   Identifaction
    -   [ ] Ensemble forest?
    -   [ ] Smoothing is important?
    -   [ ] Check change point algorithm
-   Visualize data gaps
-   Features
    -   [ ] Thickness in N direction
    -   [ ] Use high resolution data for feature extraction
-   Compare with other methods of identifying IDs
    -   [ ] Verify with other methods of identifying IDs
-   [x] Incorporate solar wind propagation model
    -   [x] Verify with solar wind propagation model
        -   [x] Coordinate transformation

## Infos

```{python}
# | label: tbl-missions
# | tbl-cap: Missions info
import yaml
import polars as pl
from functools import reduce
from great_tables import GT

with open("data/info.yml", "r") as file:
    data = yaml.safe_load(file)

# Recursive function to find magnetometers
def find_instrument(instruments, ins_type):
    instrument = {}
    for key, value in instruments.items():
        if value.get("type") == ins_type:
            instrument = value
        elif "instruments" in value:
            instrument = find_instrument(value["instruments"], ins_type)
    return instrument

def parse_yaml(data, info, ins_type=None):
    rows = []

    for mission, details in data["missions"].items():
        if ins_type is None:
            rows.append([mission, details.get(info)])
            continue
        instruments = details.get("instruments", {})
        instrument = find_instrument(instruments, ins_type)
        rows.append([mission, instrument.get(info)])

    return pl.DataFrame(rows, schema=["Mission", info])

# Define the merge function
def merge_dfs(left: pl.DataFrame, right, on="Mission", how="outer_coalesce"):
    return left.join(right, on=on, how=how)

# Parse and display the table
df_mag = parse_yaml(data, "time_resolutions", "magnetometer").rename(
    {"time_resolutions": "δt(B)"}
)
df_plasma = parse_yaml(data, "time_resolutions", "plasma").rename(
    {"time_resolutions": "δt(plasma)"}
)
df_r = parse_yaml(data, "radial_coverage")
df_time = parse_yaml(data, "launch_date")
df_link = parse_yaml(data, "website")

df_list = [df_mag, df_plasma, df_r, df_time, df_link]  # Replace with your DataFrames

df_merged = reduce(merge_dfs, df_list).with_columns(pl.col("website").list.join(", "))

GT(df_merged.to_pandas()).fmt_markdown("website").cols_label(
    radial_coverage="Radial coverage",
    launch_date="Launch date",
)
```
